# Descriptive statistics

```{r message=F,warning=F}
library(psych)
library(haven)
library(tidyverse)
library(labelled)
library(brms)
library(Hmisc)
library(table1)
set.seed(3103)
```

## Importing and preparing the data


```{r}
d <- haven::read_sav("data/original/Users Germany.sav")
```

Selecting only the variables of interest

```{r}
d1 <- d %>% 
  select(
         first_operator=anbiet1,
         age = v29,
         gender = v28,
         income = v32,
         education = v30,
         frequency_modes = v08_10, #private car
         public_transport = v05, #transport public ticket
         frequency_modes_before_cs = v17_20, #private car
         n_cars_no_cs = v18,
         city = ort,
         n_cars = v03,
         children = v02_1,
         household_size = v01)
```

Basic transformations

Let's convert everything to numeric (to get rid of the labels from SPSS).

Then we recode the answers so we have more descriptive labels for the table.
```{r}
d2 <- as.data.frame(sapply(d1, as.numeric))
#gender
d2$gender<-as.character(d2$gender)
d2$gender <- dplyr::recode(d2$gender, 
                 '1'='Male',
                 '2'='Female',
                 '3'='Other')
d2$gender <- as.factor(d2$gender)
#age
d2$age <- 2019 - d2$age
d2$age_c <- scale(d2$age)

#income
d2$income <- na_if(d2$income, 9)
d2$income <- as.character(d2$income)
income_order <-c('< 1000',
                 '1000 to 2000',
                 '2000 to 3000',
                 '3000 to 4000',
                 '4000 to 5000',
                 '> 5000')
d2$income <- dplyr::recode(d2$income, 
                 '1'='< 1000',
                 '2'='1000 to 2000',
                 '3'='2000 to 3000',
                 '4'='3000 to 4000',
                 '5'='4000 to 5000',
                 '6'='> 5000')
d2$income <- factor(d2$income, levels = income_order, ordered = T)

#first operator
d2$first_operator <- na_if(d2$first_operator, 9)#no information
d2$first_operator <- na_if(d2$first_operator, 10) #drivenow
d2$first_operator <- na_if(d2$first_operator, 11) #flinkster
d2$first_operator <- na_if(d2$first_operator, 99) #other
d2$first_operator <- as.character(d2$first_operator)
d2$first_operator <- dplyr::recode(d2$first_operator, 
                 '1'='COMB', #book n drive     
                 '2'='RTSB_B', #stadmobil,
                 '3'='RTSB_A',#cambio
                 '4'='RTSB_B', #stadmobil
                 '5'='FF', #car2go
                 '6'='P2P' #drivy
                 )
d2$first_operator <- factor(d2$first_operator, ordered = FALSE)
d2$first_operator <- as.factor(d2$first_operator)

#education
d2$education <- na_if(d2$education, 9)
d2$education <- as.character(d2$education)
education_order <-c('Secondary school 1',
                 'Secondary school 2',
                 'High school',
                 'University')
d2$education <- dplyr::recode(d2$education, 
                 '1'='Secondary school 1',
                 '2'='Secondary school 2',
                 '3'='High school',
                 '4'='University')
d2$education <- factor(d2$education, levels = education_order, ordered = T)

d2$public_transport <- as.character(d2$public_transport) 
d2$public_transport <-  dplyr::recode(d2$public_transport, 
                 '1'='Yes',   
                 '2'='No')

d2$city <- as.character(d2$city) 
d2$city <-  dplyr::recode(d2$city, 
                 '1'='Frankfurt',   
                 '2'='Köln',
                 '3'='Stuttgart',
                 '4'='Others')

d2$n_cars <- as.character(d2$n_cars)
d2$n_cars <- dplyr::recode(d2$n_cars, 
                 '1'='One car',
                 '2'='Two cars',
                 '3'='Three or more cars',
                 '4'='No car')
n_car_order <-c('No car',
                 'One car',
                 'Two cars',
                 'Three or more cars')
d2$n_cars <- factor(d2$n_cars, levels = n_car_order, ordered = T)



d2$n_cars_no_cs <- as.character(d2$n_cars_no_cs)
d2$n_cars_no_cs <- dplyr::recode(d2$n_cars_no_cs, 
                 '1'='One car',
                 '2'='Two cars',
                 '3'='Three or more cars',
                 '4'='No car',
                 '5'='Do not know')
n_cars_no_cs_order <-c('No car',
                 'One car',
                 'Two cars',
                 'Three or more cars',
                 'Do not know')

d2$n_cars_no_cs <- factor(d2$n_cars_no_cs, levels = n_cars_no_cs_order, ordered = T)

d2$children <- as.character(d2$children) 
d2$children <-  dplyr::recode(d2$children, 
                 '0'='Yes',   
                 '1'='No')


d2$household_size <- as.character(d2$household_size)
d2$household_size <- dplyr::recode(d2$household_size, 
                 '1'='1',
                 '2'='2',
                 '3'='3',
                 '4'='4',
                 '5'='> 5')
household_size_order <-c('1','2','3','4','> 5')
d2$household_size <- factor(d2$household_size, levels = household_size_order, ordered = T)

d2$frequency_modes <- as.character(d2$frequency_modes)
d2$frequency_modes <- dplyr::recode(d2$frequency_modes, 
                 '1'='Daily',
                 '2'='4-6 days a week',
                 '3'='1-3 days a week',
                 '4'='Do not know')
frequency_modes_order <-c('Daily','4-6 days a week','1-3 days a week','Do not know')
d2$frequency_modes <- factor(d2$frequency_modes, levels = frequency_modes_order, ordered = T)


d2$frequency_modes_before_cs <- as.character(d2$frequency_modes_before_cs)
d2$frequency_modes_before_cs <- dplyr::recode(d2$frequency_modes_before_cs, 
                 '1'='Less often than today',
                 '2'='About as often as today',
                 '3'='More often than today',
                 '4'='Less frequently',
                 '5'='Never')
frequency_modes_before_cs_order <-c('Daily','4-6 days a week','1-3 days a week','Less frequently','Never')
d2$frequency_modes_before_cs <- factor(d2$frequency_modes_before_cs, levels = frequency_modes_before_cs_order, ordered = T)

```


## Descriptive statistics table

Now let's create a table of with the descriptive statistics.

```{r cache=F}
table1::label(d2$city) <-  "City"
table1::label(d2$age) <- "Age" 
table1::label(d2$gender) <- "Gender"
table1::label(d2$education) <- "Education"
table1::label(d2$income) <- "Household income before taxes (euro)"
table1::label(d2$household_size) <- "Household (number of persons cohabiting)"
table1::label(d2$children) <- "Presence of children in the household"
table1::label(d2$n_cars) <-  "Current number of cars in the household with carsharing membership"
table1::label(d2$n_cars_no_cs) <- "Expected number of cars in the household without carsharing membership"
table1::label(d2$frequency_modes) <- "Frequency of use of private car"
table1::label(d2$public_transport) <- "Ownership of monthly PT ticket"
table1::label(d2$first_operator) <- "Main carsharing operator"
```

```{r}
table1::table1(~ city+age+gender+education+income+household_size+children, data=d2,caption="Socio-demographic descriptive statistics of the sample") %>% t1kable()
```
```{r}
table1::table1(~ n_cars+n_cars_no_cs+frequency_modes+public_transport | first_operator, data=d2,caption="Descriptive statistics of private car use across carsharing business models") %>% t1kable()
```

## Tables for the paper

```{r echo=T, results='hide'}
table1::table1(~ city+age+gender+education+income+household_size+children, data=d2,caption="Socio-demographic descriptive statistics of the sample") %>% t1kable(booktabs = T,format = 'latex', label='descriptive-socio')
```

```{r echo=T, results='hide'}
table1::table1(~ n_cars+n_cars_no_cs+frequency_modes+public_transport|first_operator, data=d2,caption="Descriptive statistics of private car use across carsharing business models") %>% t1kable(booktabs = T,format = 'latex', label='descriptive-car')
```
