# Ranking carsharing based on the type of the trip

```{r}
library(haven)
library(tidyverse)
library(labelled)
library(bpcs)
library(knitr)
set.seed(3103)
```


## Importing the data

```{r}
d <- haven::read_sav("data/original/Users Germany.sav")
```

## Helper functions

Here we define some initial functions to help make the paired comparison. These function basically take 1 row and create a dataset with all 10 possible paired comparisons. Then it merges each of these new datasets together.

```{r}
# expand 1 row
process_row <- function(df, out, company0, company1, row){
  diff01 <- df[[row,company0]] - df[[row,company1]]
  
  if(!is.na(diff01)){
      res<-NULL
      if(diff01==0)
        res <- rbinom(1,1,0.5)#if tie it is randomly solved
      else
        res <- ifelse(diff01 > 0 , 0, 1)
      out <- add_row(out,company0=company0,company1=company1, win=res, user=row)
  }

    return(out)
}

convert2pairedcomp <- function(df){
  out<-tribble(~company0, ~company1, ~win, ~user)
  i<-1
  for(i in seq_along(1:nrow(df))){
    # print(i)
    # All 10 combinations
    out <- process_row(df,out, 'COMB','FF',i)
    out <- process_row(df,out, 'COMB','RTSB_B',i)
    out <- process_row(df,out, 'COMB','P2P',i)
    out <- process_row(df,out, 'COMB','RTSB_A',i)
  
    out <- process_row(df,out, 'FF','RTSB_B',i)
    out <- process_row(df,out, 'FF','P2P',i)
    out <- process_row(df,out, 'FF','RTSB_A',i)
  
    out <- process_row(df,out, 'RTSB_B','P2P',i)
    out <- process_row(df,out, 'RTSB_B','RTSB_A',i)
  
    out <- process_row(df,out, 'P2P','RTSB_A',i)
  }
  return(out)
}

```

## Number of people registered in at least 2 companies

Here we just calculate how many people are registered in at least 2-5 companies (among all users)

```{r}
d_registered_in_2<- d %>% 
  select(anbiet1, anbiet2, anbiet3, anbiet4, anbiet5, anbiet6) %>% 
  filter(!is.na(anbiet1)&!is.na(anbiet2))


cat('There are:', nrow(d_registered_in_2), ' registered in at least 2 companies\n')

d_registered_in_3 <- d %>% 
  select(anbiet1, anbiet2, anbiet3, anbiet4, anbiet5, anbiet6) %>% 
  filter(!is.na(anbiet1)&!is.na(anbiet2)&!is.na(anbiet3))


cat('There are:', nrow(d_registered_in_3), ' registered in at least 3 companies\n')

d_registered_in_4 <- d %>% 
  select(anbiet1, anbiet2, anbiet3, anbiet4, anbiet5, anbiet6) %>% 
  filter(!is.na(anbiet1)&!is.na(anbiet2)&!is.na(anbiet3)&!is.na(anbiet4))

cat('There are:', nrow(d_registered_in_4), ' registered in at least 4 companies\n')

d_registered_in_5 <- d %>% 
  select(anbiet1, anbiet2, anbiet3, anbiet4, anbiet5, anbiet6) %>% 
  filter(!is.na(anbiet1)&!is.na(anbiet2)&!is.na(anbiet3)&!is.na(anbiet4)&!is.na(anbiet5))

cat('There are:', nrow(d_registered_in_5), ' registered in at least 5 companies\n')

```



## Work trips

```{r}
d_work <- d %>% 
  select(v22bnd_1,
         v22c2g_1,
         v22stamo,
         v22driv,
         v22cam_1) %>% 
  rename('COMB'='v22bnd_1',
        'FF' ='v22c2g_1',
        'RTSB_B' = 'v22stamo',
        'P2P' = 'v22driv',
        'RTSB_A' = 'v22cam_1') %>% 
  mutate(COMB = as.numeric(COMB),
         FF = as.numeric(FF),
         RTSB_B = as.numeric(RTSB_B),
         P2P = as.numeric(P2P),
         RTSB_A = as.numeric(RTSB_A))
```

Now lets convert this to paired comparison
```{r}
d_work_pc <- convert2pairedcomp(d_work)
cat(length(unique(d_work_pc$user)), ' evaluated at least two companies')
```

```{r eval=F, cache=T, message=F}
m_work <- bpc(d_work_pc,
             player0 = 'company0', 
             player1='company1', 
             result_column = 'win', 
             model_type = 'bt')
saveRDS(m_work,file = 'models/m_work.RDS')
```

```{r echo=F, eval=T}
m_work <- readRDS('models/m_work.RDS')
```


```{r}
plot(m_work)
```

```{r}
summary(m_work)
```


## Going out for dinner trips
```{r}
d_dinner <- d %>% 
  select(v22bnd_2,
         v22c2g_2,
         v158_a,
         v164_a,
         v22cam_2) %>% 
  rename('COMB'='v22bnd_2',
        'FF' ='v22c2g_2',
        'RTSB_B' = 'v158_a',
        'P2P' = 'v164_a',
        'RTSB_A' = 'v22cam_2') %>% 
  mutate(COMB = as.numeric(COMB),
         FF = as.numeric(FF),
         RTSB_B = as.numeric(RTSB_B),
         P2P = as.numeric(P2P),
         RTSB_A = as.numeric(RTSB_A))
```

Now lets convert this to paired comparison
```{r}
d_dinner_pc <- convert2pairedcomp(d_dinner)
```

```{r cache=T, message=F, eval=F}
m_dinner <- bpc(d_dinner_pc,
             player0 = 'company0', 
             player1='company1', 
             result_column = 'win', 
             model_type = 'bt')
saveRDS(m_dinner,file = 'models/m_dinner.RDS')
```

```{r echo=F, eval=T}
m_dinner <- readRDS('models/m_dinner.RDS')
```

```{r}
plot(m_dinner)
```

```{r}
summary(m_dinner)
```


## Daily-shopping trips

```{r}
d_shopdaily <- d %>% 
  select(v22bnd_3,
         v22c2g_3,
         v159_a,
         v165_a,
         v22cam_3) %>% 
  rename('COMB'='v22bnd_3',
        'FF' ='v22c2g_3',
        'RTSB_B' = 'v159_a',
        'P2P' = 'v165_a',
        'RTSB_A' = 'v22cam_3') %>% 
  mutate(COMB = as.numeric(COMB),
         FF = as.numeric(FF),
         RTSB_B = as.numeric(RTSB_B),
         P2P = as.numeric(P2P),
         RTSB_A = as.numeric(RTSB_A))
```

Now lets convert this to paired comparison
```{r}
d_shopdaily_pc <- convert2pairedcomp(d_shopdaily)
cat(length(unique(d_shopdaily_pc$user)), ' evaluated at least two companies')
```

```{r cache=T, message=F, eval=F}
m_shopdaily <- bpc(d_shopdaily_pc,
             player0 = 'company0', 
             player1='company1', 
             result_column = 'win', 
             model_type = 'bt')
saveRDS(m_shopdaily,file = 'models/m_shopdaily.RDS')
```

```{r echo=F, eval=T}
m_shopdaily <- readRDS('models/m_shopdaily.RDS')
```


```{r}
plot(m_shopdaily)
```

```{r}
summary(m_shopdaily)
```


## Bulk shopping trips

```{r}
d_shopbulk <- d %>% 
  select(v22bnd_4,
         v22c2g_4,
         v160_a,
         v166_a,
         v22cam_4) %>% 
  rename('COMB'='v22bnd_4',
        'FF' ='v22c2g_4',
        'RTSB_B' = 'v160_a',
        'P2P' = 'v166_a',
        'RTSB_A' = 'v22cam_4') %>% 
  mutate(COMB = as.numeric(COMB),
         FF = as.numeric(FF),
         RTSB_B = as.numeric(RTSB_B),
         P2P = as.numeric(P2P),
         RTSB_A = as.numeric(RTSB_A))
```

Now lets convert this to paired comparison
```{r}
d_shopbulk_pc <- convert2pairedcomp(d_shopbulk)
cat(length(unique(d_shopbulk_pc$user)), ' evaluated at least two companies')
```

```{r cache=T, message=F, eval=F}
m_shopbulk <- bpc(d_shopbulk_pc,
             player0 = 'company0', 
             player1='company1', 
             result_column = 'win', 
             model_type = 'bt')
saveRDS(m_shopbulk,file = 'models/m_shopbulk.RDS')
```

```{r echo=F, eval=T}
m_shopbulk <- readRDS('models/m_shopbulk.RDS')
```


```{r}
plot(m_shopbulk)
```

```{r}
summary(m_shopbulk)
```


## Recreational activity trips

```{r}
d_recreational <- d %>% 
  select(v22bnd_5,
         v22c2g_5,
         v161_a,
         v167_a,
         v22cam_5) %>% 
  rename('COMB'='v22bnd_5',
        'FF' ='v22c2g_5',
        'RTSB_B' = 'v161_a',
        'P2P' = 'v167_a',
        'RTSB_A' = 'v22cam_5') %>% 
  mutate(COMB = as.numeric(COMB),
         FF = as.numeric(FF),
         RTSB_B = as.numeric(RTSB_B),
         P2P = as.numeric(P2P),
         RTSB_A = as.numeric(RTSB_A))
```

Now lets convert this to paired comparison
```{r}
d_recreational_pc <- convert2pairedcomp(d_recreational)
cat(length(unique(d_recreational_pc$user)), ' evaluated at least two companies')
```

```{r cache=T, message=F, eval=F}
m_recreational <- bpc(d_recreational_pc,
             player0 = 'company0', 
             player1='company1', 
             result_column = 'win', 
             model_type = 'bt')
saveRDS(m_recreational,file = 'models/m_recreational.RDS')
```

```{r echo=F, eval=T}
m_recreational <- readRDS('models/m_recreational.RDS')
```


```{r}
plot(m_recreational)
```

```{r}
summary(m_recreational)
```

## Holiday trips

```{r}
d_holidays <- d %>% 
  select(v22bnd_6,
         v22c2g_6,
         v162_a,
         v168_a,
         v22cam_6) %>% 
  rename('COMB'='v22bnd_6',
        'FF' ='v22c2g_6',
        'RTSB_B' = 'v162_a',
        'P2P' = 'v168_a',
        'RTSB_A' = 'v22cam_6') %>% 
  mutate(COMB = as.numeric(COMB),
         FF = as.numeric(FF),
         RTSB_B = as.numeric(RTSB_B),
         P2P = as.numeric(P2P),
         RTSB_A = as.numeric(RTSB_A))
```

Now lets convert this to paired comparison
```{r}
d_holidays_pc <- convert2pairedcomp(d_holidays)
cat(length(unique(d_holidays_pc$user)), ' evaluated at least two companies')
```

```{r cache=T, message=F, eval=F}
m_holidays <- bpc(d_holidays_pc,
             player0 = 'company0', 
             player1='company1', 
             result_column = 'win', 
             model_type = 'bt')
saveRDS(m_holidays,file = 'models/m_holidays.RDS')
```

```{r echo=F, eval=T}
m_holidays <- readRDS('models/m_holidays.RDS')
```

```{r}
plot(m_holidays)
```

```{r}
summary(m_holidays)
```

## Creating tables and figures for the article

Table of ranks

```{r cache=T}
rank_table <- rbind( get_rank_of_players_df(m_work),
                     get_rank_of_players_df(m_dinner),
                     get_rank_of_players_df(m_shopdaily),
                     get_rank_of_players_df(m_shopbulk),
                     get_rank_of_players_df(m_recreational),
                     get_rank_of_players_df(m_holidays))
colnames(rank_table) <- c('Carsharing', 'Median', 'Mean', 'sd')

rank_table$Carsharing <- str_remove(rank_table$Carsharing, fixed('lambda['))
rank_table$Carsharing <- str_remove(rank_table$Carsharing, fixed(']'))

rank_table %>% kable(caption="Rank of the types of carsharing", 
                     booktabs=T, 
                     digits =2, 
                     format = 'html',
                     label='ranking-table') %>% 
  kableExtra::kable_styling() %>%
  kableExtra::pack_rows("Work trips", 1, 5) %>%
  kableExtra::pack_rows("Dinner trips", 6, 10) %>%
  kableExtra::pack_rows("Daily shopping trips", 11, 15) %>%
  kableExtra::pack_rows("Bulk shopping trips",  16, 20) %>%
  kableExtra::pack_rows("Recreational trips", 21, 25) %>%
  kableExtra::pack_rows("Holiday trips", 26, 30)
  
```

