# Psychological predictors of carsharing per business model

```{r}
library(psych)
library(haven)
library(tidyverse)
library(labelled)
library(brms)
library(knitr)
set.seed(3103)
```


## Importing the data

```{r}
d <- haven::read_sav("data/original/Users Germany.sav")
```

Selecting the relevant variables for this analysis.

```{r echo=F}
d1 <- d %>% 
  select(
    #dv
    freq_car2go=v19ff_10,
    freq_bookndrive=v19ff_20,
    freq_stadtmobil=v19ff_30,
    # freq_flinkster=v19ff_40,
    freq_drivy_or_snappcar=v19ff_50,
    freq_car2go_or_drivenow=v19k_10,
    freq_cambio=v19k_20,
    # freq_flinkster2=v19k_30,
    freq_drivy_or_snappcar2=v19k_40,
    freq_car2go2=v19s_10,
    freq_stadtmobil2=v19s_20,
    # freq_flinkster3=v19s_30,
    freq_drivy_or_snappcar3=v19s_40,
    #habits
    habit_q1=v07_10,
    habit_q2=v07_20,
    habit_q3=v07_30,
    habit_q4=v07_40,
    habit_q5=v07_50,
    habit_q6=v07_60,
    habit_q7=v07_70,
    habit_q8=v07_80,
    #climate morality
    climate_q1=v34_10,
    climate_q2=v34_20,
    climate_q3=v35_10,
    climate_q4=v35_20,
    climate_q5=v35_30,
    #subjective norms
    subj_q1=v36_20,
    subj_q2=v36_30,
    subj_q3=v36_40,
    #trust
    trust_q1=v26_10,
    trust_q2=v26_20,
    trust_q3=v26_30,
    #control
    control_q1=v25_10,
    control_q2=v25_20,
    control_q3=v25_30,
    control_q4=v25_40,
    control_q5=v25_50,
    control_q6=v25_60,
    #age
    age = v29,
    #gender
    gender = v28,
    #income
    income = v32,
    #education
    education = v30
    )  %>% 
  #here we are coalescing (merging in a single column where we have null and keeping the first value if there are more than one for the same row)
  mutate(FF = coalesce(freq_car2go, freq_car2go_or_drivenow,freq_car2go2),
         RTSB_B = coalesce(freq_stadtmobil, freq_stadtmobil2),
         COMB = freq_bookndrive,
         RTSB_A = freq_cambio,
         P2P = coalesce(freq_drivy_or_snappcar, freq_drivy_or_snappcar2, freq_drivy_or_snappcar3)) %>% 
  select(-starts_with('freq_'))

```

Let's convert everything to numeric to get rid of the labels and process some of the other variables
```{r}
d2 <- as.data.frame(sapply(d1, as.numeric))
#gender
d2$gender <- na_if(d2$gender, 3)#there are only 3 cases of other
d2$gender<-as.character(d2$gender)
d2$gender <- dplyr::recode(d2$gender, 
                 '1'='Male',
                 '2'='Female',
                 '3'='Other')
d2$gender <- as.factor(d2$gender)
#age
d2$age <- 2019 - d2$age
d2$age_c <- scale(d2$age)

#income
d2$income <- na_if(d2$income, 9)
d2$income <- as.character(d2$income)
income_order <-c('less_1000',
                 '1000_to_2000',
                 '2000_to_3000',
                 '3000_to_4000',
                 '4000_to_5000',
                 'greater_5000')
d2$income <- dplyr::recode(d2$income, 
                 '1'='less_1000',
                 '2'='1000_to_2000',
                 '3'='2000_to_3000',
                 '4'='3000_to_4000',
                 '5'='4000_to_5000',
                 '6'='greater_5000')
d2$income <- factor(d2$income, levels = income_order, ordered = T)

#education
d2$education <- na_if(d2$education, 9)
d2$education <- as.character(d2$education)
education_order <-c('SecondarySchool_1',
                 'SecondarySchool_2',
                 'Highschool',
                 'University')
d2$education <- dplyr::recode(d2$education, 
                 '1'='SecondarySchool_1',
                 '2'='SecondarySchool_2',
                 '3'='Highschool',
                 '4'='University')
d2$education <- factor(d2$education, levels = education_order, ordered = T)

```

Finally let's consider only the complete cases in the predictors

```{r}
dropna_cols <-c(
  #habits
  'habit_q1',
  'habit_q2',
  'habit_q3',
  'habit_q4',
  'habit_q5',
  'habit_q6',
  'habit_q7',
  'habit_q8',
  #climate morality
  'climate_q1',
  'climate_q2',
  'climate_q3',
  'climate_q4',
  'climate_q5',
  #subjective norms
  'subj_q1',
  'subj_q2',
  'subj_q3',
  #trust
  'trust_q1',
  'trust_q2',
  'trust_q3',
  #control
  'control_q1',
  'control_q2',
  'control_q3',
  'control_q4',
  'control_q5',
  'control_q6',
  #others
  'age_c',
  'income',
  'education',
  'gender'
)

d3 <- tidyr::drop_na(d2, tidyselect::any_of(dropna_cols))
```

We moved from 1121 cases to 762 cases when selecting only complete cases there.


## Factor analysis

To do a factor analysis with ordinal values we need to do a polychoric factor analysis or a non-linear FA. In this case we will do a polychoric factor analysis

### Habits

```{r}
habits <- d3 %>%
  select(starts_with('habit'))
```

Getting the scree plot

```{r cache=T}
#Getting the polychoric correlation
habits_poly_cor <- polychoric(habits)
fa.parallel(habits, fa='fa', cor='poly')
habits_model = fa(habits, nfactor=1, cor="poly", fm="mle", rotate = "none")
```

Showing the loadings of the factor analysis
```{r}
print(habits_model)
```


### Climate

```{r}
climate <- d3 %>%
  select(starts_with('climate'))
```

Getting the scree plot

```{r cache=T}
#Getting the polychoric correlation
climate_poly_cor <- polychoric(climate)
fa.parallel(climate, fa='fa', cor='poly')
climate_model = fa(climate, nfactor=1, cor="poly", fm="mle", rotate = "none")
```

Showing the loadings of the factor analysis
```{r}
print(climate_model)
```


### Subjective norms

```{r}
subj <- d3 %>%
  select(starts_with('subj'))
```

Getting the scree plot

```{r cache=T}
#Getting the polychoric correlation
subj_poly_cor <- polychoric(subj)
fa.parallel(subj, fa='fa', cor='poly')
subj_model = fa(subj, nfactor=1, cor="poly", fm="mle", rotate = "none")
```

Showing the loadings of the factor analysis
```{r}
print(subj_model)
```


### Trust

```{r}
trust <- d3 %>%
  select(starts_with('trust'))
```

Getting the scree plot

```{r cache=T}
#Getting the polychoric correlation
trust_poly_cor <- polychoric(trust)
fa.parallel(trust, fa='fa', cor='poly')
trust_model = fa(trust, nfactor=1, cor="poly", fm="mle", rotate = "none")
```


Showing the loadings of the factor analysis
```{r}
print(trust_model)
```


### Control

```{r}
control <- d3 %>%
  select(starts_with('control'))
```

Getting the scree plot

```{r cache=T}
#Getting the polychoric correlation
control_poly_cor <- polychoric(control)
fa.parallel(control, fa='fa', cor='poly')
control_model = fa(control, nfactor=1, cor="poly", fm="mle", rotate = "none")
```

Showing the loadings of the factor analysis
```{r}
print(control_model)
```


### Table for the Lambda's

```{r warning=F,message=F}
habits_lambda <- psych::guttman(habits_poly_cor$rho)
climate_lambda <- psych::guttman(climate_poly_cor$rho)
subj_lambda <- psych::guttman(subj_poly_cor$rho)
trust_lambda <- psych::guttman(trust_poly_cor$rho)
control_lambda <- psych::guttman(control_poly_cor$rho)
lambda <- data.frame(Lambda=c("Chronbach's Alpha (Lambda 3)", "Lambda 4"),
                     Habits = c(habits_lambda$lambda.3, habits_lambda$lambda.4),
                     Climate = c(climate_lambda$lambda.3, climate_lambda$lambda.4),
                     "Subjective" = c(subj_lambda$lambda.3, subj_lambda$lambda.4),
                     Trust = c(trust_lambda$lambda.3, trust_lambda$lambda.4),
                     Control = c(control_lambda$lambda.3, control_lambda$lambda.4))
```

```{r}
lambda %>% kable(caption="Values of the Lambda 3 and Lambda 4 of Guttman for the psychological predictors",
                 digits = 2,
                 format='html',
                 booktabs=T,
                 label="rq4-lambda")
```

```{r echo=F, results='hide'}
lambda %>% kable(caption="Values of the Lambda 3 and Lambda 4 of Guttman for the psychological predictors",
                 digits = 2,
                 format='latex',
                 booktabs=T,
                 label="rq4-lambda")
```


### Adding the FA scores to data frame

Now we need to add to the data frame the actual scores obtained by the FA
```{r}
add_scores_to_df <- function(df, fa_model,name){
  scores<- as.data.frame(fa_model$scores)
  n <- ncol(scores)
  names_col<-NULL
  if(n>1)
    names_col <- paste(rep('fa_', n),
                       rep(name, n),
                       seq(1,n),
                       sep = "")
  else
    names_col <- paste('fa_',name,sep="")
  colnames(scores) <- names_col
  out <- cbind(df,scores)
  return(out)
}
```

```{r}
d3 <- add_scores_to_df(d3, habits_model, 'habits')
d3 <- add_scores_to_df(d3, climate_model, 'climate')
d3 <- add_scores_to_df(d3, subj_model, 'subj')
d3 <- add_scores_to_df(d3, trust_model, 'trust')
d3 <- add_scores_to_df(d3, control_model, 'control')
```


### Selecting only the relevant variables now

```{r}
d4 <- d3 %>% 
  select(
  FF,
  RTSB_B,
  COMB,
  RTSB_A,
  P2P,
  starts_with('fa'),
  age_c,
  education,
  gender,
  income
)
```


## Analysis and models

Now we are going to do the same analysis for each car sharing type company

We are using the same weakly informative priors for all models. For the monotonic predictors we are using the default priors where the distance is the same between each item in the income and education scale
```{r}
priors<-c(set_prior("normal(0,5)", class = "b", coef = "fa_habits"),
          set_prior("normal(0,5)", class = "b", coef = "fa_climate"),
          set_prior("normal(0,5)", class = "b", coef = "fa_subj"),
          set_prior("normal(0,5)", class = "b", coef = "fa_trust"),
          set_prior("normal(0,5)", class = "b", coef = "fa_control"),
          set_prior("normal(0,5)", class = "b", coef = "age_c"),
          set_prior("normal(0,5)", class = "b", coef = "genderMale"))
priors0<-c(set_prior("normal(0,5)", class = "b", coef = "age_c"),
          set_prior("normal(0,5)", class = "b", coef = "genderMale"))
```




### FF

```{r}
d_ff <- d4 %>% 
  select(FF,
         starts_with('fa'),
         age_c,
         gender,
         education,
         income) %>% 
  drop_na()

d_ff$FF <- as.ordered(d_ff$FF)
```

Ordinal regression with monotonic predictors

```{r echo=T, eval=F}
m_ff <- brm(FF ~ fa_habits + fa_climate + fa_subj + fa_trust + fa_control + gender + mo(income) + age_c + mo(education),
            data = d_ff,
            prior = priors,
            family = cumulative(),
            cores=4
            )
m_ff0 <- brm(FF ~ gender + mo(income) + age_c + mo(education),
            data = d_ff,
            prior = priors0,
            family = cumulative(),
            cores=4
            )
saveRDS(m_ff0, 'models/m_ff0.RDS')
saveRDS(m_ff, 'models/m_ff.RDS')
```

```{r eval=T, echo=F}
m_ff <- readRDS('models/m_ff.RDS')
m_ff0 <- readRDS('models/m_ff0.RDS')
```

Now we can get the summary of the model
```{r}
summary(m_ff)
```

#### Comparing the two models

```{r cache=T, message=F, warning=F}
WAIC(m_ff)
WAIC(m_ff0)
```

#### Marginal effects 

In these sequence of plots we plot the conditional effects on how changing one variable impacts the probability of choosing one of the five items (1-5) in the frequency of using a carsharing type/company

```{r cache=T}
plot(conditional_effects(m_ff, categorical = T), ask=F)
```

### RTSB_A

```{r}
d_rtsba <- d4 %>% 
  select(RTSB_A,
         starts_with('fa'),
         age_c,
         gender,
         education,
         income) %>% 
  drop_na()

d_rtsba$RTSB_A <- as.ordered(d_rtsba$RTSB_A)
```

Ordinal regression with monotonic predictors

```{r echo=T, eval=F}
m_rtsba <- brm(RTSB_A ~ fa_habits + fa_climate + fa_subj + fa_trust + fa_control + gender + mo(income) + age_c + mo(education),
            data = d_rtsba,
            prior = priors,
            family = cumulative(),
            cores=4
            )
saveRDS(m_rtsba, 'models/m_rtsba.RDS')

m_rtsba0 <- brm(RTSB_A ~  gender + mo(income) + age_c + mo(education),
            data = d_rtsba,
            prior = priors0,
            family = cumulative(),
            cores=4
            )
saveRDS(m_rtsba0, 'models/m_rtsba0.RDS')
```

```{r eval=T, echo=F}
m_rtsba <- readRDS('models/m_rtsba.RDS')
m_rtsba0 <- readRDS('models/m_rtsba0.RDS')
```

Now we can get the summary of the model
```{r}
summary(m_rtsba)
```

#### Comparing the two models

```{r cache=T, message=F, warning=F}
WAIC(m_rtsba)
WAIC(m_rtsba0)
```


#### Marginal effects 

In these sequence of plots we plot the conditional effects on how changing one variable impacts the probability of choosing one of the five items (1-5) in the frequency of using a carsharing type/company

```{r cache=T}
plot(conditional_effects(m_rtsba, categorical = T), ask=F)
```


### RTSB_B

```{r}
d_rtsbb <- d4 %>% 
  select(RTSB_B,
         starts_with('fa'),
         age_c,
         gender,
         education,
         income) %>% 
  drop_na()

d_rtsbb$RTSB_B <- as.ordered(d_rtsbb$RTSB_B)
```

Ordinal regression with monotonic predictors

```{r echo=T, eval=F}
m_rtsbb <- brm(RTSB_B ~ fa_habits + fa_climate + fa_subj + fa_trust + fa_control + gender + mo(income) + age_c + mo(education),
            data = d_rtsbb,
            prior = priors,
            family = cumulative(),
            cores=4
            )
saveRDS(m_rtsbb, 'models/m_rtsbb.RDS')

m_rtsbb0 <- brm(RTSB_B ~ gender + mo(income) + age_c + mo(education),
            data = d_rtsbb,
            prior = priors0,
            family = cumulative(),
            cores=4
            )
saveRDS(m_rtsbb0, 'models/m_rtsbb0.RDS')
```

```{r eval=T, echo=F}
m_rtsbb <- readRDS('models/m_rtsbb.RDS')
m_rtsbb0 <- readRDS('models/m_rtsbb0.RDS')
```

Now we can get the summary of the model
```{r}
summary(m_rtsbb)
```

#### Comparing the two models

```{r cache=T, message=F, warning=F}
WAIC(m_rtsbb)
WAIC(m_rtsbb0)
```


#### Marginal effects 

In these sequence of plots we plot the conditional effects on how changing one variable impacts the probability of choosing one of the five items (1-5) in the frequency of using a carsharing type/company

```{r cache=T}
plot(conditional_effects(m_rtsbb, categorical = T), ask=F)
```

### COMB

```{r}
d_comb <- d4 %>% 
  select(COMB,
         starts_with('fa'),
         age_c,
         gender,
         education,
         income) %>% 
  drop_na()

d_comb$COMB <- as.ordered(d_comb$COMB)
```

Ordinal regression with monotonic predictors

```{r echo=T, eval=F}
m_comb <- brm(COMB ~ fa_habits + fa_climate + fa_subj + fa_trust + fa_control + gender + mo(income) + age_c + mo(education),
            data = d_comb,
            prior = priors,
            family = cumulative(),
            cores=4
            )
saveRDS(m_comb, 'models/m_comb.RDS')
m_comb0 <- brm(COMB ~  gender + mo(income) + age_c + mo(education),
            data = d_comb,
            prior = priors0,
            family = cumulative(),
            cores=4
            )
saveRDS(m_comb0, 'models/m_comb0.RDS')
```

```{r eval=T, echo=F}
m_comb <- readRDS('models/m_comb.RDS')
m_comb0 <- readRDS('models/m_comb0.RDS')
```

Now we can get the summary of the model
```{r}
summary(m_comb)
```

#### Comparing the two models

```{r cache=T, message=F, warning=F}
WAIC(m_comb)
WAIC(m_comb0)
```


#### Marginal effects 

In these sequence of plots we plot the conditional effects on how changing one variable impacts the probability of choosing one of the five items (1-5) in the frequency of using a carsharing type/company

```{r cache=T}
plot(conditional_effects(m_comb, categorical = T), ask=F)
```

### P2P
```{r}
d_p2p <- d4 %>% 
  select(P2P,
         starts_with('fa'),
         age_c,
         gender,
         education,
         income) %>% 
  drop_na()

d_p2p$P2P <- as.ordered(d_p2p$P2P)
```

Ordinal regression with monotonic predictors

```{r echo=T, eval=F}
m_p2p <- brm(P2P ~ fa_habits + fa_climate + fa_subj + fa_trust + fa_control + gender + mo(income) + age_c + mo(education),
            data = d_p2p,
            prior = priors,
            family = cumulative(),
            cores=4
            )
saveRDS(m_p2p, 'models/m_p2p.RDS')
m_p2p0 <- brm(P2P ~  gender + mo(income) + age_c + mo(education),
            data = d_p2p,
            prior = priors0,
            family = cumulative(),
            cores=4
            )
saveRDS(m_p2p0, 'models/m_p2p0.RDS')
```

```{r eval=T, echo=F}
m_p2p <- readRDS('models/m_p2p.RDS')
m_p2p0 <- readRDS('models/m_p2p0.RDS')
```

Now we can get the summary of the model
```{r}
summary(m_p2p)
```

#### Comparing the two models

```{r cache=T, message=F, warning=F}
WAIC(m_p2p)
WAIC(m_p2p0)
```


#### Marginal effects 

In these sequence of plots we plot the conditional effects on how changing one variable impacts the probability of choosing one of the five items (1-5) in the frequency of using a carsharing type/company

```{r cache=T}
plot(conditional_effects(m_p2p, categorical = T), ask=F)
```


## Figures for the paper

### Habits panel

```{r results='hide'}
habits_ff <- plot(conditional_effects(m_ff, effects="fa_habits",categorical = T))[[1]] + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Habits",
       title = "FF",
       fill = "Response",
       colour = "Response")+
  theme(axis.title.x=element_blank())

habits_rtsba <- plot(conditional_effects(m_rtsba, effects="fa_habits",categorical = T))[[1]] +
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Habits",
       title = "RTSB_A",
       fill = "Response",
       colour = "Response")+ 
  theme(axis.title.x=element_blank(),
        axis.text.y = element_blank(),
        axis.title.y=element_blank())

habits_rtsbb <- plot(conditional_effects(m_rtsbb, effects="fa_habits",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Habits",
       title = "RTSB_B",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.y=element_blank(),
        axis.text.y = element_blank())

habits_comb <- plot(conditional_effects(m_comb, effects="fa_habits",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Habits",
       title = "COMB",
       fill = "Response",
       colour = "Response")+ 
    theme(axis.title.x=element_blank(),
          axis.text.y = element_blank(),
          axis.title.y=element_blank())

habits_p2p <- plot(conditional_effects(m_p2p, effects="fa_habits",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Habits",
       title = "P2P",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.x=element_blank(), 
        axis.text.y = element_blank(),
        axis.title.y=element_blank())
```

### Climate panel
```{r results='hide'}
climate_ff <- plot(conditional_effects(m_ff, effects="fa_climate",categorical = T))[[1]] + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Climate",
       fill = "Response",
       colour = "Response")+
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),)

climate_rtsba <- plot(conditional_effects(m_rtsba, effects="fa_climate",categorical = T))[[1]] +
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Climate",
       fill = "Response",
       colour = "Response")+ 
  theme(axis.title.x=element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_blank(),
        axis.title.y=element_blank())

climate_rtsbb <- plot(conditional_effects(m_rtsbb, effects="fa_climate",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Climate",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.y=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank())

climate_comb <- plot(conditional_effects(m_comb, effects="fa_climate",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Climate",
       fill = "Response",
       colour = "Response")+ 
    theme(axis.title.x=element_blank(),
          plot.title = element_blank(),
          axis.text.y = element_blank(),
          axis.title.y=element_blank())

climate_p2p <- plot(conditional_effects(m_p2p, effects="fa_climate",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Climate",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y=element_blank())
```

### Subjective norm panel
```{r results='hide'}
subjective_ff <- plot(conditional_effects(m_ff, effects="fa_subj",categorical = T))[[1]] + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Subjective norm",
       fill = "Response",
       colour = "Response")+
  theme(axis.title.x=element_blank(),
        plot.title = element_blank())

subjective_rtsba <- plot(conditional_effects(m_rtsba, effects="fa_subj",categorical = T))[[1]] +
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Subjective norm",
       fill = "Response",
       colour = "Response")+ 
  theme(axis.title.x=element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_blank(),
        axis.title.y=element_blank())

subjective_rtsbb <- plot(conditional_effects(m_rtsbb, effects="fa_subj",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Subjective norm",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.y=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank())

subjective_comb <- plot(conditional_effects(m_comb, effects="fa_subj",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Subjective norm",
       fill = "Response",
       colour = "Response")+ 
    theme(axis.title.x=element_blank(),
          plot.title = element_blank(),
          axis.text.y = element_blank(),
          axis.title.y=element_blank())

subjective_p2p <- plot(conditional_effects(m_p2p, effects="fa_subj",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Subjective norm",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y=element_blank())
```

### Trust panel
```{r results='hide'}
trust_ff <- plot(conditional_effects(m_ff, effects="fa_trust",categorical = T))[[1]] + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Trust",
       fill = "Response",
       colour = "Response")+
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),)

trust_rtsba <- plot(conditional_effects(m_rtsba, effects="fa_trust",categorical = T))[[1]] +
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Trust",
       fill = "Response",
       colour = "Response")+ 
  theme(axis.title.x=element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_blank(),
        axis.title.y=element_blank())

trust_rtsbb <- plot(conditional_effects(m_rtsbb, effects="fa_trust",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Trust",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.y=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank())

trust_comb <- plot(conditional_effects(m_comb, effects="fa_trust",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Trust",
       fill = "Response",
       colour = "Response")+ 
    theme(axis.title.x=element_blank(),
          plot.title = element_blank(),
          axis.text.y = element_blank(),
          axis.title.y=element_blank())

trust_p2p <- plot(conditional_effects(m_p2p, effects="fa_trust",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Trust",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y=element_blank())
```

### Control panel
```{r results='hide'}
control_ff <- plot(conditional_effects(m_ff, effects="fa_control",categorical = T))[[1]] + 
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Control",
       fill = "Response",
       colour = "Response")+
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),)

control_rtsba <- plot(conditional_effects(m_rtsba, effects="fa_control",categorical = T))[[1]] +
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Control",
       fill = "Response",
       colour = "Response")+ 
  theme(axis.title.x=element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_blank(),
        axis.title.y=element_blank())

control_rtsbb <- plot(conditional_effects(m_rtsbb, effects="fa_control",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Control",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.y=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank())

control_comb <- plot(conditional_effects(m_comb, effects="fa_control",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Control",
       fill = "Response",
       colour = "Response")+ 
    theme(axis.title.x=element_blank(),
          plot.title = element_blank(),
          axis.text.y = element_blank(),
          axis.title.y=element_blank())

control_p2p <- plot(conditional_effects(m_p2p, effects="fa_control",categorical = T))[[1]]+
  coord_cartesian(ylim = c(0,1)) +
  labs(x="Control",
       fill = "Response",
       colour = "Response")  + 
  theme(axis.title.x=element_blank(),
        plot.title = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y=element_blank())
```

### Merging panels

```{r}
habits <- (habits_ff + habits_rtsba + habits_rtsbb + habits_comb + habits_p2p ) + plot_layout(nrow=1)
  
climate <- (climate_ff + climate_rtsba + climate_rtsbb +climate_comb +climate_p2p)+ plot_layout(nrow=1) 

subjective <- (subjective_ff + subjective_rtsba + subjective_rtsbb +subjective_comb +subjective_p2p)+ plot_layout(nrow=1) 

trust <- (trust_ff + trust_rtsba + trust_rtsbb +trust_comb +trust_p2p)+ plot_layout(nrow=1) 


control <- (control_ff + control_rtsba + control_rtsbb + control_comb + control_p2p ) +
  plot_layout(nrow=1) 

panel <- (habits / climate/ subjective / trust /control) + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```


```{r}
panel
```

