--- 
title: 'Online appendix for the paper: "Roundtrip, free-floating and peer-to-peer carsharing: A Bayesian behavioral analysis"'
author: "Érika Martins Silva Ramos, David Issa Mattos and Cecilia Jakobsson Bergstad"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: 'This is the online appendix for the paper: "Roundtrip, free-floating and peer-to-peer carsharing: A Bayesian behavioral analysis"'
always_allow_html: true
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
knitr::opts_chunk$set(cache=TRUE)

library(bpcs)
library(tidyverse)
library(knitr)
```

# Foreword

This is the online appendix for the paper *"Roundtrip, free-floating and peer-to-peer carsharing: A Bayesian behavioral analysis"*. It contains a commented and reproducible code for all the analysis, tables and plots presented in the paper.

## Session info

This appendix is compiled automatically and the following session information was used to generate this appendix:

```{r}
sessionInfo()
```




